\documentclass{llncs}

\usepackage[backend=biber, sorting=none, style=lncs]{biblatex}
\addbibresource{test.bib}

\begin{document}

\nocite{*} biblatex:
\printbibliography

\newpage
manual:
\begin{thebibliography}{10}
% typeinst.tex
\bibitem{jour}
Smith, T.F., Waterman, M.S.:
Identification of Common Molecular Subsequences.
J. Mol. Biol. 147, 195--197 (1981)

\bibitem{lncschap}
May, P., Ehrlich, H.-C., Steinke, T.:
ZIB Structure Prediction Pipeline: Composing a Complex Biological Workflow through Web Services.
In: Nagel, W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006.
LNCS, vol. 4128, pp. 1148--1158. Springer, Heidelberg (2006)

\bibitem{book}
Foster, I., Kesselman, C.:
The Grid: Blueprint for a New Computing Infrastructure.
Morgan Kaufmann, San Francisco (1999)

\bibitem{proceeding1}
Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.:
Grid Information Services for Distributed Resource Sharing.
In: 10th IEEE International Symposium on High Performance Distributed Computing,
pp. 181--184. IEEE Press, New York (2001)

\bibitem{proceeding2}
Foster, I., Kesselman, C., Nick, J., Tuecke, S.:
The Physiology of the Grid:
an Open Grid Services Architecture for Distributed Systems Integration.
Technical report, Global Grid Forum (2002)

\bibitem{url}
National Center for Biotechnology Information,
\url{http://www.ncbi.nlm.nih.gov}

% llncs.dem
\bibitem{clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. 78, 315--333 (1982)

\bibitem{clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris 287, 1013--1015 (1978)

\bibitem{mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal period for nonautonomous Hamiltonian systems.
J. Diff. Eq. 72, 28--55 (1988)

\bibitem{tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)

\bibitem{rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. 33, 609--633 (1980)
\end{thebibliography}

\end{document}

